---
title: "HW5"
author: "jgn2108"
date: "`r Sys.Date()`"
output: github_document
---

#Problem 1: Washington Post data in a github repository
```{r}
#install.packages("readr")
#install.packages("skimr")
#library(readr)
#library(tidyverse)
#library(skimr)
```

#Read in data
```{r}
url <- "https://raw.githubusercontent.com/washingtonpost/data-homicides/master/homicide-data.csv"

# Read the CSV file into a data frame
homicide_data <- read_csv(url)

# View the first few rows of the data
head(homicide_data)
```
#Data cleaning (using skimr)
```{r}
# Use the skim() function directly from skimr without loading the whole package
skim_summary <- skimr::skim(homicide_data)

# Print the summary
print(skim_summary)

```
#Convert tibble into a standard df
```{r}
homicide_data_df <- as.data.frame(homicide_data)
str(homicide_data_df)
```
This data represents the names and demographics of homicide victims across the U.S., as well as the date the homicide was reported, the location (latitude/longitude) the victims were found, and the disposition of the case (i.e., whether an arrest was made or not).


